Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-01-03 Cost_manuscript.Rmd
updating figs

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort
  and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
- \usepackage{indentfirst}
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
  word_document: #default
    reference_docx: Style_reference_draft.docx
  html_document:
    df_print: paged
csl: apa.csl
indent: true
bibliography: cost_paper.bib
---

@@

@@

@@

```{r General prop & earnings plots (Fig. 3), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost. Middle: Total number of dollars earned by each group by the end of the experiment. Right: The relationship between proportion accepted and total earned. Consistent with the foraging design, participants who over and under accepted earned the least."}
# plots generated in 16.2.1. and 16.1.3.
 prop1 | earnings1 | earnFitplot_btw
```

@@

``` {r BTW: 16.2.4. Plot Deviance comparison, echo = FALSE, fig.align = "center", fig.width = 6,fig.height = 4}
# plot AIC and BIC
ABIC_plot_btw <- ME_evals$abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare_btw))) %>%
  ggplot(aes(Model, Value, fill = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
      theme(legend.position = c(0.8, 0.7),
            axis.text.x = element_text(angle = 45, hjust = 1),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line = element_line(colour = "black"),
            text = element_text(size = 22))

@@

```{r mixed effects plots (Fig. 4), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination. A: Proportion accepted by each group for every combination of handling time and reward. Grey dots indicate the reward-maximizing acceptance for each combination. B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition (crosses mark non-significant comparisons). Each entry shows how much more likely a group was to accept compared to the reference condition (row). C: AIC and BIC values for a forward mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model."}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG4.png")
```

>>>>

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort
  and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
- \usepackage{indentfirst}
output:
  word_document: #default
    reference_docx: Style_reference_draft.docx
  pdf_document:
    highlight: haddock
    keep_tex: no
  html_document:
    df_print: paged
csl: apa.csl
indent: true
bibliography: cost_paper.bib
---

@@

include_graphics("./Images/FIG1_task_a.png")
```

@@

include_graphics("./Images/FIG1_task_b.png")
```

@@

```{r General prop & earnings plots (Fig. 3), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost. Middle: Total number of dollars earned by each group by the end of the experiment. Right: The relationship between proportion accepted and total earned. Consistent with the foraging design, participants who over and under accepted earned the least."}
# plots generated in 16.2.1. and 16.1.3.
#(propPlot <- prop1 | earnings1 | earnFitplot_btw)
#ggsave("./Images/FIG3_props.png", propPlot, device = "png", height = 4, width = 10)

include_graphics("./Images/FIG3_props.png")

@@

``` {r BTW: 16.2.4. Plot Deviance comparison, echo = FALSE, fig.align = "center", fig.width = 6,fig.height = 4}
# plot AIC and BIC
ABIC_plot_btw <- ME_evals$abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare_btw))) %>%
  ggplot(aes(Model, Value, group = Comparison, fill = Comparison)) +
    geom_line(aes(color = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
    labs(x = "", y = "") +
    scale_x_discrete(labels = c("Base", "Cost", "Handling", "Offer", "H + R", "All Main", "H + R Int.", "Full Interaction")) +
    theme(legend.position = c(0.8, 0.7),
          axis.text.x = element_text(angle = 30, hjust = 1),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(colour = "black"),
          legend.key=element_blank(),
          text = element_text(size = 20))

@@

```{r mixed effects plots (Fig. 4), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination. A: Proportion accepted by each group for every combination of handling time and reward. Grey dots indicate the reward-maximizing acceptance for each combination. B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition (crosses mark non-significant comparisons). Each entry shows how much more likely a group was to accept compared to the reference condition (row). C: AIC and BIC values for a forward mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model."}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG4_btwlogistic.png")
```
